### 2018-11-30 manuscript/manuscript.rmd
stuff

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	#dplyr::rename(matrix=dataset) %>% 
	dplyr::rename(gene=cluster_number)

>>>>

partition_map_global = 
	read_tsv("../reconciliation/blast/graphs/diamond_partition_clusters.tsv") %>%
	dplyr::rename(partition=partition_name) %>%
	dplyr::rename(gene=cluster_number) %>%
	mutate( gene = as.character(gene) )
